---
output:
  rmarkdown::github_document
bibliography: "README-refs.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`ctmle3`: modern Super Learning with pipelines

[![Travis-CI Build Status](https://travis-ci.org/tlverse/ctmle3.svg?branch=master)](https://travis-ci.org/tlverse/ctmle3)
[![Build status](https://ci.appveyor.com/api/projects/status/lfv64jnygnmx6txi?svg=true)](https://ci.appveyor.com/project/jeremyrcoyle/ctmle3)
[![Coverage Status](https://img.shields.io/codecov/c/github/tlverse/ctmle3/master.svg)](https://codecov.io/github/tlverse/ctmle3?branch=master)
<!-- [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active) -->
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
<!-- [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.1342294.svg)](https://doi.org/10.5281/zenodo.1342294) -->
<!-- [![Join the chat at https://gitter.im/ctmle3-Rpkg/Lobby](https://badges.gitter.im/ctmle3-Rpkg/Lobby.svg)](https://gitter.im/ctmle3-Rpkg/Lobby?utm_source=badge&utm_medium=badge&utm_campaign=pr-badge&utm_content=badge) -->

> A modern implementation of the Collaborative Targeted Maximum Likelihood Estimator (C-TMLE) algorithm for xxxxx

__Authors:__ [Weixin Cai](https://github.com/wilsoncai1992), [Jeremy Coyle](https://github.com/jeremyrcoyle)

---

## What's `ctmle3`?

<!-- `ctmle3` is a modern implementation of the Super Learner algorithm of
@vdl2007super. The Super Learner algorithm performs ensemble learning in one of
two fashions:

1. The _discrete_ Super Learner can be used to select the best prediction
   algorithm from among a supplied library of machine learning algorithms
   ("learners" in the `ctmle3` nomenclature) -- that is, the discrete Super Learner
   is the single learning algorithm that minimizes the cross-validated risk with
   respect to an appropriate loss function.
2. The _ensemble_ Super Learner can be used to assign weights to a set of
   specified learning algorithms (from a user-supplied library of such
   algorithms) so as to create a combination of these learners that minimizes
   the cross-validated risk with respect to an appropriate loss function. This
   notion of weighted combinations has also been referred to as _stacked
   regression_ [@breiman1996stacked] and _stacked generalization_
   [@wolpert1992stacked].
 -->
---

## Installation

<!--
For standard use, we recommend installing the package from
[CRAN](https://cran.r-project.org/) via

```{r cran-installation, eval = FALSE}
install.packages("ctmle3")
```
-->

Install the most recent _stable release_ from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/):

```{r gh-master-installation, eval = FALSE}
devtools::install_github("tlverse/ctmle3")
```

---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/tlverse/ctmle3/issues).

---

## Examples

<!-- `ctmle3` makes the process of applying screening algorithms, learning algorithms,
combining both types of algorithms into a stacked regression model, and
cross-validating this whole process essentially trivial. The best way to
understand this is to see the `ctmle3` package in action:

```{r ctmle3-simple-example}
set.seed(49753)
suppressMessages(library(data.table))
library(dplyr)
library(SuperLearner)
library(origami)
library(ctmle3)

# load example data set
data(cpp)
cpp <- cpp %>%
  dplyr::filter(!is.na(haz)) %>%
  mutate_all(funs(replace(., is.na(.), 0)))

# use covariates of intest and the outcome to build a task object
covars <- c("apgar1", "apgar5", "parity", "gagebrth", "mage", "meducyrs",
            "sexn")
task <- ctmle3_Task$new(cpp, covariates = covars, outcome = "haz")

# set up screeners and learners via built-in functions and pipelines
slscreener <- Lrnr_pkg_SuperLearner_screener$new("screen.glmnet")
glm_learner <- Lrnr_glm$new()
screen_and_glm <- Pipeline$new(slscreener, glm_learner)
SL.glmnet_learner <- Lrnr_pkg_SuperLearner$new(SL_wrapper = "SL.glmnet")

# stack learners into a model (including screeners and pipelines)
learner_stack <- Stack$new(SL.glmnet_learner, glm_learner, screen_and_glm)
stack_fit <- learner_stack$train(task)
preds <- stack_fit$predict()
head(preds)
```
 -->
---

## Contributions

It is our hope that `ctmle3` will grow to be widely used for creating stacked
regression models and the cross-validation of pipelines that make up such
models, as well as the variety of other applications in which the Super Learner
algorithm plays a role. To that end, contributions are very welcome, though we
ask that interested contributors consult our [contribution
guidelines](https://github.com/tlverse/ctmle3/blob/master/CONTRIBUTING.md)
prior to submitting a pull request.

---

After using the `ctmle3` R package, please cite the following:

        @misc{coyle2018ctmle3,
          author = {Cai, Weixin and Coyle, Jeremy R},
          title = {{ctmle3}: Modern Pipelines for Machine Learning and {Super
            Learning}},
          year  = {2018},
          howpublished = {\url{https://github.com/tlverse/ctmle3}},
          note = {{R} package version 0.1.0},
        }

---

## License

&copy; 2017-2018 [Weixin Cai](https://github.com/wilsoncai1992), [Jeremy R. Coyle](https://github.com/jeremyrcoyle)

The contents of this repository are distributed under the GPL-3 license. See
file `LICENSE` for details.

---

## References

